Communicating human related spatial distributions: A comparison of spatial visualisations using visual inference.

### 2020-01-05 paper/paper.tex

the difference in the detection rates for the two displays will be
compared using the following:

@@

The contributors who detected no plots correctly were analysed further.
Three of these contribuotrs gave no choices for any of the twelve
displays. They were also removed for the rest of the analysis. The
contributors who gave various plot choices and reasons for the twelve
displays were kept.

67 of the 92 participants were male, and 25 female and only two of the
participants had lived in Australia before.

70 of the participants achieved a Bachelors or Masters degree.

@@

The detection rate is used to find the accuracy for participants
reporting the real data trend model. The accuracy can be seen from many
views.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/detection_compare-1.pdf}
\caption{Contrasting the detection rate achieved by participants when
viewing the four replicates of the three trend models. Each point shows
the probability of detection for the lineup display, the facets separate
the trend models hidden in the lineup. The points for the same data set
shown in a choroleth or haxgon tile map display are linked to show the
difference in the detection rate.}
\end{figure}

>>>>

The difference in the detection rates for the two displays will be
compared using the following:

@@

The contributors who gave various plot choices and reasons for the
twelve displays were kept. The contributors who detected no plots
correctly were analysed further. Three of these contribuotrs gave no
choices for any of the twelve displays. They were also removed for the
rest of the analysis.

Of the 92 participants, 67 were male, and 25 female. Only two of the
participants had lived in Australia before. The education level achieved
by the participants was 70 Bachelors or Masters degree.

@@

The detection rate for participants reporting the real data trend model
is used to calculate the accuracy of the responses of participants.

\includegraphics{paper_files/figure-latex/detection_compare-1.pdf} The
detection rates are usually higher when participants viewed the hexagon
tile map displays. The difference was greater when viewing a three
cities trend model. When the trend model affected all cities
participants also detected the data display in the lineup of null plots
more often. The North West to South East data plot was detected with
similar rates when viewing the choropleth and hexagon tile map displays,
though for three of the replicates the participants detected the data
display more often.
